---
output: github_document
---

# StructureMC: Structured Matrix Completion

[![CRAN](https://www.r-pkg.org/badges/version/StructureMC)](https://CRAN.R-project.org/package=StructureMC)

## Overview

Current literature on matrix completion focuses primarily on independent sampling models under which the individual observed entries are sampled independently. Motivated by applications in genomic data integration, we propose a new framework of structured matrix completion (SMC) to treat structured missingness by design. Specifically, our proposed method aims at efficient matrix recovery when a subset of the rows and columns of an approximately low-rank matrix are observed. The main function in our package, `smc.FUN`, is for recovery of the missing block A22 of an approximately low-rank matrix A given the other blocks A11, A12, A21.

## Installation

Install stable version from CRAN:

```{r, eval=FALSE}
install.packages("StructureMC")
```

Install development version from GitHub:

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("celehs/StructureMC")
```

## Citation

Cai, T., Cai, T. T., & Zhang, A. (2015). Structured Matrix Completion with Applications to Genomic Data Integration. Journal of the American Statistical Association. https://doi.org/10.1080/01621459.2015.1021005
